Tree height, microhabitat, and hydraulic traits shape drought responses in a temperate broadleaf forest

### 2019-10-12 manuscript/climate_sensitivity_draft.tex
Tried fixing errors with latex

\raggedright

@@

\caption{\label{tab:unnamed-chunk-3}**Table 1. Summary of hypotheses, corresponding specific predictions, and results.** We count predictions as fully supported / rejected when the response matches/contradicts the prediction in both univariate and multivariate models (when applicable). Parentheses indicate that predictions were partially supported/ rejected--i.e., that the direction of response matched/contradicted the prediction in some but not all models.}

@@

\caption{\label{tab:unnamed-chunk-4}**Table 2. Summary of variables**}
\centering
\resizebox{\linewidth}{!}{
\fontsize{12}{14}\selectfont
\begin{tabular}{lll>{\raggedright\arraybackslash}p{7cm}llllll}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{ } & \multicolumn{1}{c}{ } & \multicolumn{1}{c}{ } & \multicolumn{1}{c}{ } & \multicolumn{1}{c}{ } & \multicolumn{3}{c}{observed values} & \multicolumn{1}{c}{ } \\
\cmidrule(l{3pt}r{3pt}){7-9}
variable & symbol & units & description & category & n & median & min & max & ln-transformed?\\
\midrule
\addlinespace[1em]
\multicolumn{1}{l}{\textbf{Dependent variable}}\\
\hspace{1em}drought resistance & R & - & ratio of growth during drought year to mean growth of the 5 years prior. & - & 1596 & 0.87 & 0 & 1.99 & no\\
\addlinespace[.4em]
\multicolumn{1}{l}{\textbf{Independent variables}}\\
\hspace{1em}drought year & Y & - & year of drought & 1966 & 478 & - & - & - & -\\
\hspace{1em} &  &  &  & 1977 & 547 & - & - & - & -\\
\hspace{1em} &  &  &  & 1999 & 571 & - & - & - & -\\
\addlinespace[.4em]
\multicolumn{1}{l}{\textit{tree size}}\\
\hspace{1em}\hspace{1em}diameter breast height & DBH & cm & DBH in drought year & - & all & 31.92 & 3.92 & 134.19 & yes\\
\hspace{1em}\hspace{1em}height & H & m & H in drought year & - & all & 20.21 & 4.76 & 43.87 & yes\\
\addlinespace[.4em]
\multicolumn{1}{l}{\textit{microhabitat}}\\
\hspace{1em}\hspace{1em}crown position & CP & - & 2018 crown position & dominant (D) & 31 & - & - & - & -\\
\hspace{1em}\hspace{1em} &  &  &  & co-dominant (C) & 231 & - & - & - & -\\
\hspace{1em}\hspace{1em} &  &  &  & intermediate (I) & 224 & - & - & - & -\\
\hspace{1em}\hspace{1em} &  &  &  & suppressed (S) & 101 & - & - & - & -\\
\hspace{1em}\hspace{1em}topographic wetness index & TWI & - & steady-state wetness index based on slope and upstream contributing area & - & all & 5.66 & 0 & 16 & yes\\
\addlinespace[.4em]
\multicolumn{1}{l}{\textit{species' traits}}\\
\hspace{1em}\hspace{1em}wood density & WD & g cm-3 & dry mass of a unit volume of fresh wood & - & all & 0.62 & 0.4 & 1.09 & no\\
\hspace{1em}\hspace{1em}leaf mass per area & LMA & kg m-2 & ratio of leaf dry mass to fresh leaf area & - & all & 48.69 & 30.68 & 75.8 & no\\
\hspace{1em}\hspace{1em}xylem porosity & X & - & vessel arrangement in xylem & ring & 408 & - &  &  & -\\
\hspace{1em}\hspace{1em} &  &  &  & semi-ring & 31 & - &  &  & -\\
\hspace{1em}\hspace{1em} &  &  &  & diffuse & 178 & - &  &  & -\\
\hspace{1em}\hspace{1em}turgor loss point & T & MPa & water potential at which leaves wilt & - & all & -2.39 & -2.76 & -1.92 & no\\
\hspace{1em}\hspace{1em}percent loss area & PLA & \% & percent loss of leaf area upon dessication & - & all & 13.06 & 8.52 & 24.64 & no\\
\bottomrule
\end{tabular}}
\end{table}

Caption: T = \(\pi_{tlp}\), X = \({XP}\)

@@

Linear mixed models were run following the order of the hypotheses as
seen in Figure ??? {[}individual\_tested\_traits{]}. Using the
\citep{R-pointRes} package, we set up models with the resistance value
as the response variable (excluding outliers with values of \(R\ge 2\)),
and each prediction's variable as the independent variable. Variables'
importance in predicting drought tolerance was calculated from
mixed-effects models and the lowest AICc
\citep[\citet{R-AICcmodavg}]{R-lme4}.Null models were determined in
order of the predictions. First, we analyzed the combined scenario to
determine if ``year'' was significant. Upon establishing this, we tested
height and DBH as size parameters. Although both were significant,
height was kept due to its larger delta AICc compared with the null
model. We then tested the remaining biophysical and hydraulic traits
individually against a null model containing height and year. This
yielded Figure ??? (cand\_full). All variables with dAICc
\textgreater{}2 were used as candidates for each scenario's best model
(figure ???? (tested\_traits\_best))

@@

In the 60-year period between 1950 and 2009, there were three droughts
that met our criteria of anomalously dry climatic conditions coupled
with substantial reductions in tree growth for at least some portions of
the community: 1966, 1977, and 1999 (Fig. 1). We excluded one year
(1991) meeting the growth reduction criteria (26.5\% of trees
experienced \textgreater{}30\% growth reduction, mean resistance=
-13.8\%) because this year was not among the strongest droughts of the
study period (\textbf{DETAILS}). Rather, the severity of growth
reduction may be explained by defoliation by gypsy moths
(\emph{Lymantria dispar} L.) from approximately 1988-1995, which most
stronly impacted \emph{Quercus} spp. (\emph{Cite Shenanadoah paper, if
accepted}). Climatically, these droughts included three of the five
years between 1950 and 2009 with greatest moisture deficit (PET-PRE)
during the peak growing season months of May-August, which are the
months to which annual tree growth at this site is most sensitive
\citep{helcoski_growing_2019}. Specifically, 1966, 1977, and 1999 had
mean MJJA PET-PRE of 83.37, 86.97, and 80 mm mo-1, respectively. The
years 1964 and 2007 also ranked in the top five driest (PET-PRE =83.87
and 82.13 mm mo-1), but \emph{were not among the lowest in terms of PDSI
and were not identified as a pointer yeasr.} \textbf{The droughts
differed in timing/duration/etc. .. The year 1966 was preceded by two
relatively dry years\ldots{} 1964 among five driest in terms of
May-August {[}PET-PRE{]}, 1965 also anomalously hot and dry. }

Community-level tree growth responses to these droughts were modest,
with modal resistance values of \#, \#, and \# for 1966, 1977, and 1999,
respectively (Fig. 1b). In each drought, roughly 30\% of the cored trees
suffered \(\ge\) 30\% growth reductions (\(R\) \(\le\) 0.7): \#\% in
1966, \#2\% un 1977, and \#\% in 1999. \emph{Some} trees exhibited
increased growth: (\(R\) \textgreater{} 1.0): \#\% in 1966, \#\% un
1977, and \#\% in 1999.

@@

\caption{\label{tab:unnamed-chunk-5}**Table 4. Univariate models**}
\centering
\resizebox{\linewidth}{!}{
\fontsize{12}{14}\selectfont
\begin{tabular}{llllrllllll}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{ } & \multicolumn{1}{c}{ } & \multicolumn{2}{c}{all droughts} & \multicolumn{2}{c}{1966} & \multicolumn{2}{c}{1977} & \multicolumn{2}{c}{1999} \\
\cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){6-7} \cmidrule(l{3pt}r{3pt}){8-9} \cmidrule(l{3pt}r{3pt}){10-11}
ï»¿variable & category & null variables & dAICc & coefficients & dAICc & coefficients & dAICc & coefficients & dAICc & coefficients\\
\midrule
drought year & 1966 &  & -2.42 & 0.0000 & - & - & - & - & - & -\\
 & 1977 &  & - & -0.0209 & - & - & - & - & - & -\\
 & 1999 &  & - & -0.0105 & - & - & - & - & - & -\\
ln[DBH] &  & Y & 8.17 & -0.0385 & 15.32 & -0.0888 & -0.87 & -0.0214 & -1.93 & 0.0057\\
ln[height] &  & Y & 8.8 & -0.0648 & 15.27 & -0.1443 & -0.98 & -0.0335 & -2.03 & 0.0018\\
\addlinespace
crown position & D & Y & -2.96 & -0.0461 & 3.25 & -0.0509 & 0.66 & -0.0759 & 0.38 & -0.0103\\
(alone) & C &  & - & 0.0000 & - & 0 & - & 0 & - & 0\\
 & I &  & - & -0.0063 & - & 0.0732 & - & -0.0298 & - & -0.0563\\
 & S &  & - & 0.0122 & - & 0.0526 & - & 0.0432 & - & -0.0483\\
crown position & D & ln[H]+Y & 0.55 & -0.0364 & -1.41 & -0.0359 & -0.24 & -0.074 & 3.99 & -0.0027\\
\addlinespace
(with height) & C &  & - & 0.0000 & - & 0 & - & 0 & - & 0\\
 & I &  & - & -0.0406 & - & 0.0177 & - & -0.0363 & - & -0.0823\\
 & S &  & - & -0.0586 & - & -0.0654 & - & 0.03 & - & -0.1011\\
ln[TWI] &  & ln[H]+Y & 5.33 & -0.0886 & -1.96 & -0.0168 & 5.06 & -0.1406 & 2.72 & -0.1025\\
ln[TWI]*ln[H] &  & ln[H]+ln[T]+Y & -1.18 & 0.0677 & -1.75 & 0.0749 & -1.86 & 0.0533 & -1.79 & 0.0566\\
\addlinespace
wood density &  & ln[H]+Y & -1.89 & -0.0498 & -1.1 & -0.2161 & -1.19 & -0.1827 & 0.23 & 0.2512\\
leaf mass per area &  & ln[H]+Y & -2 & 0.0003 & -1.89 & 0.0011 & -1.74 & -0.0014 & -1.99 & 0.0005\\
ring porosity & ring & ln[H]+Y & -2.4 & 0.0574 & 1.78 & 0.151 & 0.59 & -0.1879 & 4.25 & 0.2025\\
 & semi-ring &  & - & -0.0335 & - & -0.1324 & - & -0.1426 & - & 0.1516\\
 & diffuse &  & - & 0.0000 & - & 0 & - & 0 & - & 0\\
\addlinespace
turgor loss point &  & ln[H]+Y & 1.22 & -0.1675 & -1.78 & -0.0845 & 1.14 & -0.2432 & 0.06 & -0.1749\\
percent loss area &  & ln[H]+Y & 7.89 & -0.0138 & 9.82 & -0.0244 & -0.07 & -0.0104 & -0.73 & -0.0074\\
\bottomrule
\end{tabular}}
\end{table}

@@

\caption{\label{tab:unnamed-chunk-6}**Table 5. Summary of R^2 and coefficients of the best multivariate models for each drought instance.** Models are ranked by AIC, and we show all models whose AIC value falls within 2.0 of the best model ($dAICc<2$).}
\centering
\resizebox{\linewidth}{!}{
\fontsize{12}{14}\selectfont
\begin{tabular}{lrrrlllllllllll}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{ } & \multicolumn{1}{c}{ } & \multicolumn{1}{c}{ } & \multicolumn{1}{c}{ } & \multicolumn{4}{c}{crown position} & \multicolumn{1}{c}{ } & \multicolumn{3}{c}{xylem architecture} & \multicolumn{1}{c}{ } & \multicolumn{1}{c}{ } \\
\cmidrule(l{3pt}r{3pt}){6-9} \cmidrule(l{3pt}r{3pt}){11-13}
ï»¿drought & dAICc & R2 & Intercept & ln[H] & D & C & I & S & ln[TWI] & diffuse & semi-ring & ring & PLA & TLP\\
\midrule
\addlinespace[.4em]
\multicolumn{1}{l}{\textbf{}}\\
\hspace{1em}all & 0.000 & 0.11 & 1.108 & -0.062 & - & - & - & - & -0.085 & - & - & - & -0.012 & -0.105\\
\hspace{1em} & 0.338 & 0.10 & 1.494 & -0.097 & -0.036 & 0 & -0.038 & -0.056 & -0.078 & - & - & - & -0.013 & -\\
\hspace{1em} & 0.403 & 0.12 & 1.263 & -0.096 & -0.035 & 0 & -0.036 & -0.053 & -0.078 & - & - & - & -0.012 & -0.087\\
\hspace{1em} & 0.515 & 0.12 & 1.393 & -0.064 & - & - & - & - & -0.087 & 0 & 0.147 & 0.048 & -0.017 & -\\
\hspace{1em} & 0.571 & 0.10 & 1.375 & -0.061 & - & - & - & - & -0.085 & - & - & - & -0.013 & -\\
\hspace{1em} & 0.903 & 0.12 & 1.492 & -0.098 & -0.034 & 0 & -0.036 & -0.053 & -0.079 & 0 & 0.122 & 0.049 & -0.016 & -\\
\addlinespace[.4em]
\hline
\multicolumn{1}{l}{\textbf{}}\\
\hspace{1em}1996 & 0.000 & 0.26 & 2.271 & -0.153 & - & - & - & - & - & 0 & 0.35 & 0.152 & -0.035 & 0.25\\
\hspace{1em} & 0.537 & 0.26 & 1.537 & -0.154 & - & - & - & - & - & 0 & 0.098 & 0.133 & -0.023 & -\\
\hspace{1em} & 1.093 & 0.27 & 2.389 & -0.177 & -0.038 & 0 & 0.016 & -0.068 & - & 0 & 0.352 & 0.153 & -0.035 & 0.27\\
\hspace{1em} & 1.434 & 0.24 & 1.629 & -0.143 & - & - & - & - & - & - & - & - & -0.024 & -\\
\hspace{1em} & 1.982 & 0.26 & 2.307 & -0.152 & - & - & - & - & -0.016 & 0 & 0.356 & 0.152 & -0.035 & 0.254\\
\addlinespace[.4em]
\hline
\multicolumn{1}{l}{\textbf{}}\\
\hspace{1em}1977 & 0.000 & 0.22 & 0.346 & - & -0.074 & 0 & -0.027 & 0.042 & -0.131 & 0 & -0.331 & -0.23 & - & -0.384\\
\hspace{1em} & 0.090 & 0.21 & 0.393 & - & - & - & - & - & -0.14 & 0 & -0.324 & -0.234 & - & -0.369\\
\hspace{1em} & 1.116 & 0.21 & 0.460 & -0.026 & - & - & - & - & -0.137 & 0 & -0.316 & -0.225 & - & -0.367\\
\hspace{1em} & 1.914 & 0.22 & 0.367 & -0.006 & -0.073 & 0 & -0.029 & 0.037 & -0.13 & 0 & -0.33 & -0.229 & - & -0.383\\
\addlinespace[.4em]
\hline
\multicolumn{1}{l}{\textbf{}}\\
\hspace{1em}1999 & 0.000 & 0.25 & 1.284 & -0.081 & 0.003 & 0 & -0.077 & -0.095 & -0.087 & 0 & 0.22 & 0.193 & -0.008 & -\\
\hspace{1em} & 0.085 & 0.25 & 0.844 & -0.082 & 0.001 & 0 & -0.078 & -0.095 & -0.085 & 0 & 0.062 & 0.185 & - & -0.142\\
\hspace{1em} & 0.462 & 0.23 & 1.174 & -0.083 & 0.002 & 0 & -0.079 & -0.099 & -0.088 & 0 & 0.135 & 0.2 & - & -\\
\hspace{1em} & 0.956 & 0.24 & 1.042 & - & - & - & - & - & -0.1 & 0 & 0.261 & 0.191 & -0.01 & -\\
\hspace{1em} & 1.029 & 0.24 & 0.700 & -0.09 & -0.002 & 0 & -0.082 & -0.101 & - & 0 & 0.046 & 0.185 & - & -0.151\\
\hspace{1em} & 1.193 & 0.24 & 1.159 & -0.089 & 0 & 0 & -0.081 & -0.101 & - & 0 & 0.21 & 0.194 & -0.008 & -\\
\hspace{1em} & 1.326 & 0.24 & 0.533 & - & - & - & - & - & -0.098 & 0 & 0.077 & 0.181 & - & -0.161\\
\hspace{1em} & 1.849 & 0.26 & 1.046 & -0.079 & 0.002 & 0 & -0.077 & -0.094 & -0.086 & 0 & 0.14 & 0.188 & -0.005 & -0.078\\
\hspace{1em} & 1.851 & 0.22 & 1.045 & -0.092 & -0.001 & 0 & -0.084 & -0.105 & - & 0 & 0.123 & 0.201 & - & -\\
\bottomrule
\end{tabular}}
\end{table}

\raggedright

>>>>

@@

\caption{\label{tab:Table 1}**Table 1. Summary of hypotheses, corresponding specific predictions, and results.** We count predictions as fully supported / rejected when the response matches/contradicts the prediction in both univariate and multivariate models (when applicable). Parentheses indicate that predictions were partially supported/ rejected--i.e., that the direction of response matched/contradicted the prediction in some but not all models.}

@@

\caption{\label{tab:Table 2}**Table 2. Summary of variables**}
\centering
\resizebox{\linewidth}{!}{
\fontsize{12}{14}\selectfont
\begin{tabular}{lll>{\raggedright\arraybackslash}p{7cm}llllll}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{ } & \multicolumn{1}{c}{ } & \multicolumn{1}{c}{ } & \multicolumn{1}{c}{ } & \multicolumn{1}{c}{ } & \multicolumn{3}{c}{observed values} & \multicolumn{1}{c}{ } \\
\cmidrule(l{3pt}r{3pt}){7-9}
variable & symbol & units & description & category & n & median & min & max & ln-transformed?\\
\midrule
\addlinespace[1em]
\multicolumn{1}{l}{\textbf{Dependent variable}}\\
\hspace{1em}drought resistance & R & - & ratio of growth during drought year to mean growth of the 5 years prior. & - & 1596 & 0.87 & 0 & 1.99 & no\\
\addlinespace[.4em]
\multicolumn{1}{l}{\textbf{Independent variables}}\\
\hspace{1em}drought year & Y & - & year of drought & 1966 & 478 & - & - & - & -\\
\hspace{1em} &  &  &  & 1977 & 547 & - & - & - & -\\
\hspace{1em} &  &  &  & 1999 & 571 & - & - & - & -\\
\addlinespace[.4em]
\multicolumn{1}{l}{\textit{tree size}}\\
\hspace{1em}\hspace{1em}diameter breast height & DBH & cm & DBH in drought year & - & all & 31.92 & 3.92 & 134.19 & yes\\
\hspace{1em}\hspace{1em}height & H & m & H in drought year & - & all & 20.21 & 4.76 & 43.87 & yes\\
\addlinespace[.4em]
\multicolumn{1}{l}{\textit{microhabitat}}\\
\hspace{1em}\hspace{1em}crown position & CP & - & 2018 crown position & dominant (D) & 31 & - & - & - & -\\
\hspace{1em}\hspace{1em} &  &  &  & co-dominant (C) & 231 & - & - & - & -\\
\hspace{1em}\hspace{1em} &  &  &  & intermediate (I) & 224 & - & - & - & -\\
\hspace{1em}\hspace{1em} &  &  &  & suppressed (S) & 101 & - & - & - & -\\
\hspace{1em}\hspace{1em}topographic wetness index & TWI & - & steady-state wetness index based on slope and upstream contributing area & - & all & 5.66 & 0 & 16 & yes\\
\addlinespace[.4em]
\multicolumn{1}{l}{\textit{species' traits}}\\
\hspace{1em}\hspace{1em}wood density & WD & g cm-3 & dry mass of a unit volume of fresh wood & - & all & 0.62 & 0.4 & 1.09 & no\\
\hspace{1em}\hspace{1em}leaf mass per area & LMA & kg m-2 & ratio of leaf dry mass to fresh leaf area & - & all & 48.69 & 30.68 & 75.8 & no\\
\hspace{1em}\hspace{1em}xylem porosity & XP & - & vessel arrangement in xylem & ring & 408 & - &  &  & -\\
\hspace{1em}\hspace{1em} &  &  &  & semi-ring & 31 & - &  &  & -\\
\hspace{1em}\hspace{1em} &  &  &  & diffuse & 178 & - &  &  & -\\
\hspace{1em}\hspace{1em}turgor loss point & $\pi_{tlp}$ & MPa & water potential at which leaves wilt & - & all & -2.39 & -2.76 & -1.92 & no\\
\hspace{1em}\hspace{1em}percent loss area & PLA & % & percent loss of leaf area upon dessication & - & all & 13.06 & 8.52 & 24.64 & no\\
\bottomrule
\end{tabular}}
\end{table}

@@

Linear mixed models were run following the order of the hypotheses as
seen in Figure ??? {[}individual\_tested\_traits{]}. Using the
\citep{R-pointRes} package, we set up models with the resistance value
as the response variable (excluding outliers with values of \(R\ge 2\)),
and each prediction's variable as the independent variable. Variables'
importance in predicting drought tolerance was calculated from
mixed-effects models and the lowest AICc
\citep[\citet{R-AICcmodavg}]{R-lme4}.Null models were determined in
order of the predictions. First, we analyzed the combined scenario to
determine if ``year'' was significant. Upon establishing this, we tested
height and DBH as size parameters. Although both were significant,
height was kept due to its larger delta AICc compared with the null
model. We then tested the remaining biophysical and hydraulic traits
individually against a null model containing height and year. This
yielded Figure ??? (candfull). All variables with dAICc \textgreater{} 2
were used as candidates for each scenario's best model (figure ????
(tested traits best))

@@

In the 60-year period between 1950 and 2009, there were three droughts
that met our criteria of anomalously dry climatic conditions coupled
with substantial reductions in tree growth for at least some portions of
the community: 1966, 1977, and 1999 (Fig. 1). We excluded one year
(1991) meeting the growth reduction criteria (26.5\% of trees
experienced \textgreater{}30\% growth reduction, mean resistance=
-13.8\%) because this year was not among the strongest droughts of the
study period (\textbf{DETAILS}). Rather, the severity of growth
reduction may be explained by defoliation by gypsy moths
(\emph{Lymantria dispar} L.) from approximately 1988-1995, which most
stronly impacted \emph{Quercus} spp. (\emph{Cite Shenandoah paper, if
accepted}). Climatically, these droughts included three of the five
years between 1950 and 2009 with greatest moisture deficit (PET-PRE)
during the peak growing season months of May-August, which are the
months to which annual tree growth at this site is most sensitive
\citep{helcoski_growing_2019}. Specifically, 1966, 1977, and 1999 had
mean MJJA PET-PRE of 83.37, 86.97, and 80 mm mo-1, respectively. The
years 1964 and 2007 also ranked in the top five driest (PET-PRE =83.87
and 82.13 mm mo-1), but \emph{were not among the lowest in terms of PDSI
and were not identified as a pointer yeasr.} \textbf{The droughts
differed in timing/duration/etc. .. The year 1966 was preceded by two
relatively dry years\ldots{} 1964 among five driest in terms of
May-August {[}PET-PRE{]}, 1965 also anomalously hot and dry. }

Community-level tree growth responses to these droughts were modest,
with modal resistance values of \#, \#, and \# for 1966, 1977, and 1999,
respectively (Fig. 1b). In each drought, roughly 30\% of the cored trees
suffered \(\ge\) 30\% growth reductions (\(R\) \(\le\) 0.7): \#\% in
1966, \#2\% un 1977, and \#\% in 1999. \emph{Some} trees exhibited
increased growth: (\(R\) \textgreater{} 1.0): \#\% in 1966, \#\% in
1977, and \#\% in 1999.

@@

\caption{\label{tab:unnamed-chunk-3}**Table 4. Univariate models**}
\centering
\resizebox{\linewidth}{!}{
\fontsize{12}{14}\selectfont
\begin{tabular}{llllrllllll}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{ } & \multicolumn{1}{c}{ } & \multicolumn{2}{c}{all droughts} & \multicolumn{2}{c}{1966} & \multicolumn{2}{c}{1977} & \multicolumn{2}{c}{1999} \\
\cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){6-7} \cmidrule(l{3pt}r{3pt}){8-9} \cmidrule(l{3pt}r{3pt}){10-11}
ï»¿variable & category & null variables & dAICc & coefficients & dAICc & coefficients & dAICc & coefficients & dAICc & coefficients\\
\midrule
drought year & 1966 &  & -2.42 & 0.0000 & - & - & - & - & - & -\\
 & 1977 &  & - & -0.0209 & - & - & - & - & - & -\\
 & 1999 &  & - & -0.0105 & - & - & - & - & - & -\\
ln[DBH] &  & Y & 8.17 & -0.0385 & 15.32 & -0.0888 & -0.87 & -0.0214 & -1.93 & 0.0057\\
ln[height] &  & Y & 8.8 & -0.0648 & 15.27 & -0.1443 & -0.98 & -0.0335 & -2.03 & 0.0018\\
\addlinespace
crown position & D & Y & -2.96 & -0.0461 & 3.25 & -0.0509 & 0.66 & -0.0759 & 0.38 & -0.0103\\
(alone) & C &  & - & 0.0000 & - & 0 & - & 0 & - & 0\\
 & I &  & - & -0.0063 & - & 0.0732 & - & -0.0298 & - & -0.0563\\
 & S &  & - & 0.0122 & - & 0.0526 & - & 0.0432 & - & -0.0483\\
crown position & D & ln[H]+Y & 0.55 & -0.0364 & -1.41 & -0.0359 & -0.24 & -0.074 & 3.99 & -0.0027\\
\addlinespace
(with height) & C &  & - & 0.0000 & - & 0 & - & 0 & - & 0\\
 & I &  & - & -0.0406 & - & 0.0177 & - & -0.0363 & - & -0.0823\\
 & S &  & - & -0.0586 & - & -0.0654 & - & 0.03 & - & -0.1011\\
ln[TWI] &  & ln[H]+Y & 5.33 & -0.0886 & -1.96 & -0.0168 & 5.06 & -0.1406 & 2.72 & -0.1025\\
ln[TWI]*ln[H] &  & ln[H]+ln[T]+Y & -1.18 & 0.0677 & -1.75 & 0.0749 & -1.86 & 0.0533 & -1.79 & 0.0566\\
\addlinespace
wood density &  & ln[H]+Y & -1.89 & -0.0498 & -1.1 & -0.2161 & -1.19 & -0.1827 & 0.23 & 0.2512\\
leaf mass per area &  & ln[H]+Y & -2 & 0.0003 & -1.89 & 0.0011 & -1.74 & -0.0014 & -1.99 & 0.0005\\
ring porosity & ring & ln[H]+Y & -2.4 & 0.0574 & 1.78 & 0.151 & 0.59 & -0.1879 & 4.25 & 0.2025\\
 & semi-ring &  & - & -0.0335 & - & -0.1324 & - & -0.1426 & - & 0.1516\\
 & diffuse &  & - & 0.0000 & - & 0 & - & 0 & - & 0\\
\addlinespace
turgor loss point &  & ln[H]+Y & 1.22 & -0.1675 & -1.78 & -0.0845 & 1.14 & -0.2432 & 0.06 & -0.1749\\
percent loss area &  & ln[H]+Y & 7.89 & -0.0138 & 9.82 & -0.0244 & -0.07 & -0.0104 & -0.73 & -0.0074\\
\bottomrule
\end{tabular}}
\end{table}

@@

\caption{\label{tab:unnamed-chunk-4}**Table 5. Summary of R\^2 and coefficients of the best multivariate models for each drought instance.** Models are ranked by AIC, and we show all models whose AIC value falls within 2.0 of the best model (dAICc<2).}
\centering
\resizebox{\linewidth}{!}{
\fontsize{12}{14}\selectfont
\begin{tabular}{lrrrlllllllllll}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{ } & \multicolumn{1}{c}{ } & \multicolumn{1}{c}{ } & \multicolumn{1}{c}{ } & \multicolumn{4}{c}{crown position} & \multicolumn{1}{c}{ } & \multicolumn{3}{c}{xylem architecture} & \multicolumn{1}{c}{ } & \multicolumn{1}{c}{ } \\
\cmidrule(l{3pt}r{3pt}){6-9} \cmidrule(l{3pt}r{3pt}){11-13}
ï»¿drought & dAICc & R2 & Intercept & ln[H] & D & C & I & S & ln[TWI] & diffuse & semi-ring & ring & PLA & TLP\\
\midrule
\addlinespace[.4em]
\multicolumn{1}{l}{\textbf{}}\\
\hspace{1em}all & 0.000 & 0.11 & 1.108 & -0.062 & - & - & - & - & -0.085 & - & - & - & -0.012 & -0.105\\
\hspace{1em} & 0.338 & 0.10 & 1.494 & -0.097 & -0.036 & 0 & -0.038 & -0.056 & -0.078 & - & - & - & -0.013 & -\\
\hspace{1em} & 0.403 & 0.12 & 1.263 & -0.096 & -0.035 & 0 & -0.036 & -0.053 & -0.078 & - & - & - & -0.012 & -0.087\\
\hspace{1em} & 0.515 & 0.12 & 1.393 & -0.064 & - & - & - & - & -0.087 & 0 & 0.147 & 0.048 & -0.017 & -\\
\hspace{1em} & 0.571 & 0.10 & 1.375 & -0.061 & - & - & - & - & -0.085 & - & - & - & -0.013 & -\\
\hspace{1em} & 0.903 & 0.12 & 1.492 & -0.098 & -0.034 & 0 & -0.036 & -0.053 & -0.079 & 0 & 0.122 & 0.049 & -0.016 & -\\
\addlinespace[.4em]
\hline
\multicolumn{1}{l}{\textbf{}}\\
\hspace{1em}1996 & 0.000 & 0.26 & 2.271 & -0.153 & - & - & - & - & - & 0 & 0.35 & 0.152 & -0.035 & 0.25\\
\hspace{1em} & 0.537 & 0.26 & 1.537 & -0.154 & - & - & - & - & - & 0 & 0.098 & 0.133 & -0.023 & -\\
\hspace{1em} & 1.093 & 0.27 & 2.389 & -0.177 & -0.038 & 0 & 0.016 & -0.068 & - & 0 & 0.352 & 0.153 & -0.035 & 0.27\\
\hspace{1em} & 1.434 & 0.24 & 1.629 & -0.143 & - & - & - & - & - & - & - & - & -0.024 & -\\
\hspace{1em} & 1.982 & 0.26 & 2.307 & -0.152 & - & - & - & - & -0.016 & 0 & 0.356 & 0.152 & -0.035 & 0.254\\
\addlinespace[.4em]
\hline
\multicolumn{1}{l}{\textbf{}}\\
\hspace{1em}1977 & 0.000 & 0.22 & 0.346 & - & -0.074 & 0 & -0.027 & 0.042 & -0.131 & 0 & -0.331 & -0.23 & - & -0.384\\
\hspace{1em} & 0.090 & 0.21 & 0.393 & - & - & - & - & - & -0.14 & 0 & -0.324 & -0.234 & - & -0.369\\
\hspace{1em} & 1.116 & 0.21 & 0.460 & -0.026 & - & - & - & - & -0.137 & 0 & -0.316 & -0.225 & - & -0.367\\
\hspace{1em} & 1.914 & 0.22 & 0.367 & -0.006 & -0.073 & 0 & -0.029 & 0.037 & -0.13 & 0 & -0.33 & -0.229 & - & -0.383\\
\addlinespace[.4em]
\hline
\multicolumn{1}{l}{\textbf{}}\\
\hspace{1em}1999 & 0.000 & 0.25 & 1.284 & -0.081 & 0.003 & 0 & -0.077 & -0.095 & -0.087 & 0 & 0.22 & 0.193 & -0.008 & -\\
\hspace{1em} & 0.085 & 0.25 & 0.844 & -0.082 & 0.001 & 0 & -0.078 & -0.095 & -0.085 & 0 & 0.062 & 0.185 & - & -0.142\\
\hspace{1em} & 0.462 & 0.23 & 1.174 & -0.083 & 0.002 & 0 & -0.079 & -0.099 & -0.088 & 0 & 0.135 & 0.2 & - & -\\
\hspace{1em} & 0.956 & 0.24 & 1.042 & - & - & - & - & - & -0.1 & 0 & 0.261 & 0.191 & -0.01 & -\\
\hspace{1em} & 1.029 & 0.24 & 0.700 & -0.09 & -0.002 & 0 & -0.082 & -0.101 & - & 0 & 0.046 & 0.185 & - & -0.151\\
\hspace{1em} & 1.193 & 0.24 & 1.159 & -0.089 & 0 & 0 & -0.081 & -0.101 & - & 0 & 0.21 & 0.194 & -0.008 & -\\
\hspace{1em} & 1.326 & 0.24 & 0.533 & - & - & - & - & - & -0.098 & 0 & 0.077 & 0.181 & - & -0.161\\
\hspace{1em} & 1.849 & 0.26 & 1.046 & -0.079 & 0.002 & 0 & -0.077 & -0.094 & -0.086 & 0 & 0.14 & 0.188 & -0.005 & -0.078\\
\hspace{1em} & 1.851 & 0.22 & 1.045 & -0.092 & -0.001 & 0 & -0.084 & -0.105 & - & 0 & 0.123 & 0.201 & - & -\\
\bottomrule
\end{tabular}}
\end{table}
